Contention management for Cloud RAN over an optical ring

### 2019-01-11 v3/articleV3.tex
avant chgt ordre

\footnote{This work was developed around the ANR N-GREEN project. The authors thank the Nokia Bell Labs team for their collaboration.} Telecommunication network providers have to design inexpensive networks supporting an increasing amount of data and online applications. Many of these applications require QoS guarantees, like minimal throughput and/or  maximal latency. The N-GREEN project aims to design a high performing optical ring while ensuring a minimal cost for providers. The current solutions with good QoS~\cite{pizzinat2015things,tayq2017real}, establish end to end direct connections (E2DE) between the nodes, which is extremely expensive. The N-GREEN optical ring is designed to ensure good performance for a low cost: the hardware it requires scales linearly with the number of nodes while E2DE scales quadratically making it impractical for more than a few nodes.

@@

Unsurprisingly, the latency of the C-RAN traffic is better when we prioritize the C-RAN messages, while the BE traffic is heavily penalized. Furthermore, there is still $10\%$ of the C-RAN traffic with a latency higher than $50 \mu$s, a problem we address in the next section. Remark that the C-RAN and BE traffic latency distribution is not the same with the FIFO method. This comes from the fact that these two sources of traffic are of different nature. With high probability, there are some part of the period which have more 
BE data arrivals (or C-RAN traffic) than average. In both cases, it makes the latency higher during these times. However a C-RAN emission from an RRH takes half the period while a BE arrival corresponds to only a few unit of times, which explains why the C-RAN traffic suffers  more from this phenomena.

@@

Figure~\ref{fig:assignment} represent an assignment of three couples RRH-BBU. each slot has a duration $F$ unit of times, and, since an RRH/BBU emits a packet each $F$ UoT during $ET$ UoT, if we take the granularity of a slot to represent the time, the emission of a BBU/RRH is continuous in the time, during $ET$ UoT. Also, if we take a date $t$ in the period $P$, then $t$ is in the slot $\frac{P}{F}$ and is at position $P \mod F$.

>>>>

\footnote{This work was developed around the ANR N-GREEN project. The authors thank the Nokia Bell Labs team for their collaboration.} Telecommunication network providers have to design inexpensive networks supporting an increasing amount of data and online applications. Many of these applications require QoS guarantees, like minimal throughput and/or  maximal latency. The N-GREEN project aims to design a high performing optical ring while ensuring a minimal cost for providers. The current solutions with good QoS~\cite{pizzinat2015things,tayq2017real}, establish end to end direct connections between the nodes, which is extremely expensive. The N-GREEN optical ring is designed to ensure good performance for a low cost: the hardware it requires scales linearly with the number of nodes while E2DE scales quadratically making it impractical for more than a few nodes.

@@

Unsurprisingly, the latency of the C-RAN traffic is better when we prioritize the C-RAN messages, while the BE traffic is heavily penalized. Furthermore, there is still $10\%$ of the C-RAN traffic with a latency higher than $50 \mu$s, a problem we address in the next section. Remark that the C-RAN and BE traffic latency distribution is not the same with the FIFO method. This comes from the fact that these two sources of traffic are of different nature. With high probability, there are some part of the period which have more 
BE data arrivals (or C-RAN traffic) than average. In both cases, it makes the latency higher during these times. Furthermore, C-RAN taffic both represent an higher load than BE traffic and it is concentrated on half the period, while BE traffic is distributed in all the period.
% However a C-RAN emission from an RRH takes half the period while a BE arrival corresponds to only a few unit of times,
It explains why the C-RAN traffic suffers more from this phenomena.
Also, we observed that the Uplink (from RRH to BBU) and Downlink (BBU to RRH) C-RAN traffics have the same latencies, that is why we chose to represent both indistinctly.

@@

Fig.~\ref{fig:assignment} represent an assignment of three couples RRH-BBU. each slot has a duration $F$ unit of times, and, since an RRH/BBU emits a packet each $F$ UoT during $ET$ UoT, if we take the granularity of a slot to represent the time, the emission of a BBU/RRH is continuous in the time, during $ET$ UoT. Also, if we take a date $t$ in the period $P$, then $t$ is in the slot $\frac{P}{F}$ and is at position $P \mod F$.
